Updated Ephemerides of the young multi-planet system V1298 Tau from TESS

### 2021-10-18 src/ms.tex
a wild figure has appeared

% Main body with filler text
\section{Introduction}
\Blindtext[4]

>>>>

% Main body with filler text
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color. Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Middle row: the \tess\ light curve with the stellar variability removed by our model. Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43. \label{fig:transits}}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
